Propaganda Films and National Identity: Animated Films in USSR and China

### 2025-03-12 paper/paper.qmd
update millionare and twister photo

Animated Film in PRC originates in the northeastern provinces colonialized by Japan [@duAnimatedEncountersTransnational2019, pp. 69]. After the world war in 1950, the communist party take over the area and transferred the Chinese and Japanese artists from Changchun to Shanghai. Like Soyuzmultfilm, a new animation studio Shanghai Film Studio was formed by joining various individual animation studio on March 24. Thew animation studio followed the cultural bureau's guideline and produces animation targeting children [@duAnimatedEncountersTransnational2019, pp. 97]. Between 1953 and 1959, inspired by the Soviet model, the government controlled all film production in mainland China, socialist realism borrowed from the Soviet Union is adopted as the dominant principle of cultural production [@duAnimatedEncountersTransnational2019, pp. 116]. Animations in this era are called the "international style", which reflect life in other countries but targets domestic audiences. From 1958, Mao launched the Great Leap Forward, with the deterioration of Sino-Soviet relations in the late 1950s, the CCP deviated from the socialist realism. In this era, elements of "revolutionary romanticism" such as myths, folklore, legends and fantasies are permitted [@duAnimatedEncountersTransnational2019, pp. 117]. Animations and propaganda incorporate traditional Chinese cultures to promote the Chinese national identity, the majorities of the stories are based in China.

@@

Mister Volk [-@gromovMisterVolk1949] is produced before the Thaw when Stalin is still in power. The director of this film work as a consulting director before producing this film, and the area of his previous productions are the animation films aimed at children based on traditional folklore. The technique used is cel animation and full animation.

![Background and characters of MrWolf are detailed and rich.](fig/wolf1.png){#fig-wolf1 width=50%}

>>>>

Animated Film in PRC originates in the northeastern provinces colonialized by Japan [@duAnimatedEncountersTransnational2019, pp. 69]. After the world war in 1950, the communist party take over the area and transferred the Chinese and Japanese artists from Changchun to Shanghai. Like Soyuzmultfilm, a new animation studio Shanghai Film Studio was formed by joining various individual animation studio on March 24. Thew animation studio followed the cultural bureau's guideline and produces animation targeting children [@duAnimatedEncountersTransnational2019, pp. 97]. Between 1953 and 1959, inspired by the Soviet model, the government controlled all film production in mainland China, socialist realism borrowed from the Soviet Union is adopted as the dominant principle of cultural production [@duAnimatedEncountersTransnational2019, pp. 116]. Animations in this era are called the "international style", which reflect life in other countries but targets domestic audiences. From 1958, Mao launched the Great Leap Forward, with the deterioration of Sino-Soviet relations in the late 1950s, the CCP deviated from the socialist realism. In this era, elements of "revolutionary romanticism" such as myths, folklore, legends, and fantasies are permitted [@duAnimatedEncountersTransnational2019, pp. 117]. Animations and propaganda incorporate traditional Chinese cultures to promote the Chinese national identity, the majorities of the stories are based in China.

@@

Mister Volk [-@gromovMisterVolk1949] is produced before the Thaw when Stalin is still in power. This is Viktor Gromov's first animated film, and the area of his previous productions are the animation films aimed at children based on traditional folklore. The director works as a consulting director for the other Soyuzmultfilm animations Little Gray Neck and The Flower with Seven Colors in 1948. The technique used in the film is cel animation and full animation. As shown in @fig-wolfa, the background of this scene is layered to produce an illusion of depth in the scene, which is a characteristic of cel animation [@pontieriSovietAnimationThaw2012b, pp. 39]. In @fig-wolfb, we observe the non linear movement between frames, this indicates full animation. There is no music played through the animation, and the overall tone focuses on an objective to uncover the dark side of American imperialism. The story is simple enough for both children and adults to understand.

::: {#fig-wolf layout-ncol=2}

![Layered background](fig/wolf1.png){#fig-wolfa}

![Fluid movement](fig/wolf2.png){#fig-wolfb}

Stills from Mister Volk
:::

Millioner [-@bordzilovskiyMillioner1963] and Mister Tvister [-@karanovichMisterTvister1963] are both produced in 1963 after the Thaw.

::: {#fig-mill layout-ncol=3}

![Characters' limited movement](fig/mill1.png){#fig-milla}

![Abstract background](fig/mill4.png){#fig-millb}

![Cutout techniques](fig/mill3.png){#fig-millc}

Stills from Millioner
:::

::: {#fig-mill layout-ncol=2}

![Characters' limited movement](fig/twis1.png){#fig-twisa}

![Abstract background](fig/twis2.png){#fig-twisb}

![Cutout techniques](fig/twis3.png){#fig-twisc}

![Cutout techniques](fig/twis4.png){#fig-twisd}

Stills from Millioner
:::
